05-exploratory_data_analysis

### 2024-11-19 scripts/05-exploratory_data_analysis.qmd
Update second draft for data and scripts
fix some bugs, add install packages step and change clean data to parquet

# Load cleaned datasets
sakura_historical_cleaned <- read_csv(here::here("data/03-cleaned_data/sakura-historical-cleaned.csv"))
sakura_modern_cleaned <- read_csv(here::here("data/03-cleaned_data/sakura-modern-cleaned.csv"))
```

>>>>

# Load cleaned datasets
sakura_historical_cleaned <-read_parquet(here::here("data/03-cleaned_data/sakura-historical-cleaned.parquet"))
sakura_modern_cleaned <- read_parquet(here::here("data/03-cleaned_data/sakura-modern-cleaned.parquet"))
```
